Can Cultural Transmission Explain The Evolution of Cooperative Behavior?

### 2020-05-16 ms/main.tex
Add figures

\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx} % Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
% TeX will automatically convert eps --> pdf in pdflatex

@@

\begin{table}[]
\begin{tabular}{|c|c|c|c|c|}
\hline
\textbf{Interaction Type} & \textbf{Frequency}    & \textbf{Fitness}      & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Probability of first interactor\\  to be A following interaction\end{tabular}}}                                                                                                     \\ \hline
\multicolumn{1}{|l|}{}    & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \textbf{\begin{tabular}[c]{@{}c@{}}Horizontal transmission\\  from partner, \\ probability $\alpha$\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Horizontal transmission \\ from population, \\ probability $1-\alpha$\end{tabular}} \\ \hline
$AxA$                     & $\hat{p}^2$           & $1+b-c$               & $1$                                                                                                               & $\hat{p}+(1-\hat{p})(1-T_B)$                                                                                           \\ \hline
$AxB$                     & $\hat{p}(1-\hat{p})$  & $1-c$                 & $1-T_B$                                                                                                           & $\hat{p}+(1-\hat{p})(1-T_B)$                                                                                           \\ \hline
$BxA$                     & $\hat{p}(1-\hat{p})$  & $1+b$                 & $T_A$                                                                                                             & $\hat{p}T_A$                                                                                                           \\ \hline
$BxB$                     & $(1-\hat{p})^2$       & $1$                   & $0$                                                                                                               & $\hat{p}T_A$                                                                                                           \\ \hline
\end{tabular}
\caption{Fitness and probabilityof first interactor to be A following interaction by interaction type}
\label{table:1}
\end{table}

\begin{figure}[b]
  \centering
  \includegraphics[scale=1]{figure.pdf}
  \caption{\textbf{Cultural horizontal transmission.} Transmission occurs between interaction partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$.}
  \label{fig:horizontal}
\end{figure}

@@

\textbf{Corollary 1.1: Equal horizontal transmission.}
If $T=T_A=T_B$, then
\begin{equation}
\label{eq:equal_transmission}
\frac{b}{c} > \frac{1-T}{\alpha T},
\end{equation}
which can be seen as a cultural version of \emph{Hamilton's rule} (eq.~\ref{eq:hamilton_rule}).

@@

Therefore, since $c>0$, cooperation will not take over the population (and furthermore will become extinct) if $T_A\leq T_B$.
When $T_A > T_B$ eq.~\ref{eq:horizontal_transmission_from_population} becomes
\begin{equation} 
\begin{split} \label{eq:horizontal_transmission_from_population_reorder}
\tilde{p} & > \frac{c\cdot(1-T_B) - (T_A-T_B)}{b\cdot(T_A-T_B)}.
\end{split}
\end{equation}
Hence, cooperation will evolve if $\tilde{p} > \tilde{p}^{*}$, which is given by
\begin{equation} 
\begin{split} \label{eq:horizontal_transmission_from_population_equilibrium}
\tilde{p}^{*} & = \frac{c\cdot(1-T_B)}{b\cdot(T_A-T_B)} - \frac{1}{b}.
\end{split}
\end{equation}
A sufficient condition for evolution of cooperation is, then,
\begin{equation} 
\begin{split} \label{eq:sufficient_horizontal_transmission_from_population}
\frac{T_A-T_B}{1-T_B} > &\ c.  
\end{split}
\end{equation}

@@

\textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype $A$ among adults increases if $p'>p$.
From eq.~\ref{eq:nextgen_parents_oblique_only}, this occurs when:
\begin{equation} \label{eq:oblique_only_result}
T_A>T_B. 
\end{equation}

>>>>

\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx} % Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
% TeX will automatically convert eps --> pdf in pdflatex
\graphicspath{ {./Figures/} }
\usepackage{subcaption}
\usepackage{float}

@@

\begin{table}[H]
\begin{tabular}{|c|c|c|c|c|}
\hline
\textbf{Interaction Type} & \textbf{Frequency}    & \textbf{Fitness}      & \multicolumn{2}{c|}{\textbf{\begin{tabular}[c]{@{}c@{}}Probability of first interactor\\  to be A following interaction\end{tabular}}}                                                                                                     \\ \hline
\multicolumn{1}{|l|}{}    & \multicolumn{1}{l|}{} & \multicolumn{1}{l|}{} & \textbf{\begin{tabular}[c]{@{}c@{}}Horizontal transmission\\  from partner, \\ probability $\alpha$\end{tabular}} & \textbf{\begin{tabular}[c]{@{}c@{}}Horizontal transmission \\ from population, \\ probability $1-\alpha$\end{tabular}} \\ \hline
$AxA$                     & $\hat{p}^2$           & $1+b-c$               & $1$                                                                                                               & $\hat{p}+(1-\hat{p})(1-T_B)$                                                                                           \\ \hline
$AxB$                     & $\hat{p}(1-\hat{p})$  & $1-c$                 & $1-T_B$                                                                                                           & $\hat{p}+(1-\hat{p})(1-T_B)$                                                                                           \\ \hline
$BxA$                     & $\hat{p}(1-\hat{p})$  & $1+b$                 & $T_A$                                                                                                             & $\hat{p}T_A$                                                                                                           \\ \hline
$BxB$                     & $(1-\hat{p})^2$       & $1$                   & $0$                                                                                                               & $\hat{p}T_A$                                                                                                           \\ \hline
\end{tabular}
\caption{Fitness and probabilityof first interactor to be A following interaction by interaction type}
\label{table:1}
\end{table}

\begin{figure}[b]
  \centering
  \includegraphics[scale=1]{figure1.pdf}
  \caption{\textbf{Cultural horizontal transmission.} Transmission occurs between interaction partners with probability $\alpha$ (left) or between two random peers with probability $1-\alpha$.}
  \label{fig:horizontal}
\end{figure}

@@

\textbf{Corollary 1.1: Equal horizontal transmission.}
If $T=T_A=T_B$, then
\begin{equation}
\label{eq:equal_transmission}
\frac{b}{c} > \frac{1-T}{\alpha T},
\end{equation}
which can be seen as a cultural version of \emph{Hamilton's rule} (eq.~\ref{eq:hamilton_rule}).
When the ratio $\frac{b}{c}$ is larger than the RHS of eq.~\ref{eq:equal_transmission} cooperation will take over of the population (see~\textbf{\autoref{fig:results_a}}).

@@

Therefore, since $c>0$, cooperation will not take over the population (and furthermore will become extinct) if $T_A\leq T_B$.
When $T_A > T_B$ eq.~\ref{eq:horizontal_transmission_from_population} becomes
\begin{equation} 
\begin{split} \label{eq:horizontal_transmission_from_population_reorder}
\tilde{p} & > \frac{c\cdot(1-T_B) - (T_A-T_B)}{b\cdot(T_A-T_B)}.
\end{split}
\end{equation}
Hence, cooperation will evolve if $\tilde{p} > \tilde{p}^{*}$ (see~\textbf{\autoref{fig:results_b}}), which is given by
\begin{equation} 
\begin{split} \label{eq:horizontal_transmission_from_population_equilibrium}
\tilde{p}^{*} & = \frac{c\cdot(1-T_B)}{b\cdot(T_A-T_B)} - \frac{1}{b}.
\end{split}
\end{equation}
A sufficient condition for evolution of cooperation is, then,
\begin{equation} 
\begin{split} \label{eq:sufficient_horizontal_transmission_from_population}
\frac{T_A-T_B}{1-T_B} > &\ c.  
\end{split}
\end{equation}

@@

\textbf{Result 2: Oblique and horizontal transmission of cooperation.} The frequency of phenotype $A$ among adults increases if $p'>p$.
From eq.~\ref{eq:nextgen_parents_oblique_only}, this occurs when:
\begin{equation} \label{eq:oblique_only_result}
T_A>T_B. 
\end{equation}
Therefore, fixation occur when $T_A>T_B$ (see~\textbf{\autoref{fig:results_c}}).

\begin{figure}[H]
  \centering
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure2a.pdf}
    \caption{$V=1$, $T_A=T_B=T$, $\alpha \neq 0$}
    \label{fig:results_a}
  \end{subfigure}
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure2b.pdf}
    \caption{$V=1$, $\alpha = 0$}
    \label{fig:results_b}
  \end{subfigure}
  \begin{subfigure}{8cm}
    \includegraphics[scale=0.5]{figure2c.pdf}
    \caption{$V=0$}
    \label{fig:results_c}
  \end{subfigure}
  \label{fig:results}
  \caption{numerical results}
\end{figure}
